The Latent Constructive Rewrite Model \\ or \\ The Latent Conceptual Grammar Model

### 2014-10-14 drafts/cfp/draft.tex
initial attempt at next sentences

Now we can describe the model we introduce here, the Latent Concept
Grammar (LCG). We introduce the LCG as a machine learning model to
learn a distribution over instances of relations over strings. Unlike
a PRCG, which places a distribution over terms $(

RCGs consist of a set
of rewrite rules, called clauses, each of which takes a termwhich
operate on a set of terms (predicates applied to arguments) to produce
new terms. Each rewrite rule is of the form:

>>>>

Now we can describe the model we introduce here, the Latent Concept
Grammar (LCG). We introduce the LCG as a machine learning model to
learn a distribution over instances of relations over strings. Unlike
a PRCG, which places a distribution over terms RCGs consist of a set
of rewrite rules, called clauses, each of which takes a termwhich
operate on a set of terms (predicates applied to arguments) to produce
new terms. Each rewrite rule is of the form:
